\documentclass{article}
\usepackage{fullpage}
\renewcommand{\thesection}{\Roman{section}}
\renewcommand{\thesubsection}{\thesection.\Roman{subsection}}
% \renewcommand{\theenumi}{\Alph{enumi}}
\usepackage{enumerate}


\title{Outline of Responsive Design}
\author{Yihong Chen, 5009 6507}
\begin{document}
\maketitle

\noindent \textbf{General Topic:} Responsive Design

\noindent \textbf{Key words:} responsive design, pixel density, display resolution, screen size, ppi

\section{Introduction}
\begin{enumerate}[A.]
\item \textbf{Attention-getter:} Have you tried to visit UBLearns on your phone?
\item \textbf{Preview:} Our class today will cover:
  \begin{itemize}
  \item Responsive design
  \item Pixel density
  \item Graph to show pixel density, screen size and different devices.
  \end{itemize}
\end{enumerate}
% \item \textbf{Preview:} We have lots of different devices today:
%   \begin{itemize}
%   \item Smartphone
%   \item Tablet
%   \item Laptop
%   \item Desktop
%   \item Smartwatch
%   \end{itemize}
% \end{enumerate}
\textbf{Transition:} You might be curious why some websites have good experience on different device. Let's move to our topic: responsive design.
\section{Body}
\begin{enumerate}[A.]
\item \textbf{Importance of term?} Various devices, more time on mobile devices.
\item \textbf{Responsive Design:} It’s a design approach to provide an optimal viewing experience
  across different devices.
  The optimal viewing experience should include readable text and image, clickable links or buttons.

  \textbf{Transition:} Let’s look at a few examples of website with no responsive design or bad responsive design:
  \begin{enumerate}[1.]
  \item UBLearns
  \item National Fuel
  \end{enumerate}

\textbf{Transition:} If you have your own website with no responsive design.
You might ask that why my pretty page looks so bad on phones.
\item \textbf{Pixel Density:} It is the number of pixels a display can fit into a fixed distance.
This is different from resolution, which is a simple count of the number of pixels across the entire display.

In some sense, we can consider resolution as population, pixel density as population density.
One country have less population doesn't mean its population density is small.

\textbf{Transition:} Now that you have a clear understanding of what responsive design is.
Let's see why it becomes so important today.
\item Show a graph of the pixel density vs screen size with different devices.
  \begin{enumerate}[1.]
  \item name: Pixel Density vs Screen Size
  \item discuss X and Y axis
  \item define ``PPI''
  \item sample point: iPhone and HDTV
  \item Trend of latest device
  \item Sum up main point
  \item Questions?
  \end{enumerate}

\end{enumerate}
\textbf{Transition:} TODO
\section{Conclusion}
\begin{enumerate}[A.]
\item cue: So, to sum up,
\item summary: today we talked the responsive design, a design approach to provide an optimal viewing experience across different devices.
\item Final words: So, when we pulish or share something to the public, we need think it over to make sure it can be diplayed correctly in different devices.
\end{enumerate}

\end{document}
